---
title: "Sample Slides for Question 10, Lab 4, 521"
subtitle: "<br/>with xaringan!"
author: "Sneha Sunil"
date: "October 1, 2022"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

class: center, middle

## Brief Course Outcomes
How to set up, manage, and use the "stack" of data science tools, Integrated Development Environments, GIT, and the Unix operating system.

---
class: center, middle

Major IDEs introduced as a part of DSCI 521  

--

JupyterLab  

--

RStudio  

--

Visual Studio Code  

--

---

## Code chunk to raise each element of the matrix to the power of 4
```{r}

data <- data.frame(x1 = 1:3,  
                   x2 = 4:6,
                   x3 = 7:9)

data <- data**4
data

```

---

### Code chunk to raise each element of the matrix to the power of 5
```{r}

data <- data.frame(x1 = 1:3,  
                   x2 = 4:6,
                   x3 = 7:9)

data <- data**5
data

```

---
class: center, middle

Thank you!

---